---
title: "NCollin_HW9_607"
author: "Noah Collin"
date: "10/23/2021"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Homework 9
**Noah Collin**
DATA 607

## Libraries:

```{r IntialLibraries}
library(tidyverse)
library(httr)
library(jsonlite)
```

## API Key:
For this homework, I'll hard code in my API Key.  If this were to be more "reproducible", I might require a user to enter their API key.

```{r APIKey}
#https://api.nytimes.com/svc/search/v2/articlesearch.json?q=election&api-key=yourkey
             
myapiKey <-  "dddddddddddddddddddddddddddddddd"

print("You're using my API key here.  Please consider using your own.  If you have one, enter it here.  Otherwise, enter nothing: ")

UserInput <- ""
UserInput <- readline();

library(stringr)
if (str_length(myapiKey)  == str_length(UserInput)) {
  myapiKey <- UserInput
  print("Thanks for using your own API key.")
} else {
  print("You're using my key still.  Please don't overuse it...")
}


```


## API Variables:

I'm going to search for the term *stenographer*.
If you're so inclined, you can change the search term, sort by newest, or change the year of search with the variables below.  Just un-comment out the comments and make them strings.  The filters tend to yield less interesting results honestly.

``` {r APICallParamaters}
searchTerm <- "stenographer"
sortNewest <- "" #"&sort=newest"
filter1 <- "" #"&fq=pub_year:(2008)"


```

## Calling the API:

```{r CallingNewYorkTimesAPI}
NYTAPIstring1 <- str_c( "https://api.nytimes.com/svc/search/v2/articlesearch.json?q=", 
                        searchTerm, 
                        filter1, 
                        sortNewest,
                        "&api-key=", 
                        myapiKey)

NYTCall1 <- GET(NYTAPIstring1, 
                verbose())

details <- content(NYTCall1, 
                   "parse")
```

## Making the DataFrame:

```{r dataframe1}

headlines <- c()
snippets <- c()
wordCounts <- c()
URLs <- c()
for (i in seq(1:10)) {
  if (length(headlines) > i-1) {
    headlines <- c()
  }
   if (length(snippets) > i-1){
    snippets <- c()
   }
   if (length(wordCounts) > i-1) {
    wordCounts <- c()
   }
     if (length(URLs) > i-1) {
    URLs <- c()
  }
  
  headlines <- c(headlines,details$response$docs[[i]]$headline$main)
  snippets <- c(snippets,details$response$docs[[i]]$snippet)
  wordCounts <- c(wordCounts,details$response$docs[[i]]$word_count)
  URLs <- c(URLs, details$response$docs[[i]]$web_url)
}

#print(length(snippets))

df1 <- data_frame("headlines" = headlines, "snippets" = snippets, "Reported Word Count" = wordCounts, "URL" = URLs)


```

## Printing the DataFrame: 
The dataframe has four relevant columns populated with the correct information.  Please note that the WordCount column seems to give odd results from the NYT API.
``` {r printDf}
print(df1)

```
